\cvsection{Referees}

% \cvref{name}{email}{mailing address}

\cvref{Principal DevOps Engr. -- Grzegorz Dubicki}
{gdubicki@egnyte.com}
{Egnyte Poland Sp. z o.o.}
\divider

\cvref{Support Manager -- Hubert Woźniak}
{hwozniak@egnyte.com}
{Egnyte Poland Sp. z o.o.}
\divider

% \cvref{IT Manager -- Łukasz Lipski}
% {lukasz.lipski@chocolissimo.pl}
% {MM Brown Sp. z o.o. }
% \divider

\cvref{CEO -- Karolina Borkowska-Pelc}
{karolina@maltaimprezy.pl}
{Malta Imprezy Sp. z o.o.}
\divider

\cvsection{DevOps motivation}
\cvachievement{\faCloud}{Why do I want to become DevOps?}{I had a great opportunity at Egnyte to work with the DevOps team on a daily basis to solve our customers' issues. In addition, I developed an application which makes our lives much easier. During my career, I worked mainly as a System Administrator, but when I had an opportunity to get a hands-on experience with DevOps tools like Kubernetes, Google Cloud, Terraform etc. I found it very interesting. In addition, the DevOps culture was what I like the most.}
\cvachievement{\faCloud}{Plan to become a DevOps Engineer.}{Although I've had already experience with CI/CD at Egnyte, I wanted to prove my qualification for this role, so I've already passed the LFCS exam and studying for the next certifications: AWS Certified Cloud Practitioner, AWS Certified SysOps Administrator - Associate and Certified Kubernetes Administrator. As the next step, I'm planning to dig much deeper into terraform, since "Infrastructure as code" seems to me a very interesting concept.}

\divider
%\cvachievement{\faLineChart}{Deliver application on Time}{ Continuously work on various platform and expand learning capability in terms of quality }



